A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-07 paper.tex
fix typo

\begin{table}[h]
	\caption{The comparism of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

@@

When a consumer request a refund, he/she need to pay 0.001 Ether additionally. Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost. Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers. However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers. This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product. Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important. An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract. Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.

>>>>

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

@@

When a consumer request a refund, he/she need to pay 0.001 Ether additionally. Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost. Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers. However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers. This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product. Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important. An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract. Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
